% slides/15_references.tex
\section*{Referencias}

\begin{frame}[allowframebreaks]{Referencias}
  \footnotesize
  \begin{thebibliography}{99}

    \bibitem{Berger1929}
    H.~Berger, ``Über das Elektrenkephalogramm des Menschen,''
    \textit{Arch. Psychiatr. Nervenkr.}, vol.~87, pp.~527--570, 1929.

    \bibitem{CooleyTukey1965}
    J.~W.~Cooley and J.~W.~Tukey, ``An algorithm for the machine calculation of complex Fourier series,''
    \textit{Math. Comput.}, vol.~19, pp.~297--301, 1965.

    \bibitem{BellSejnowski1995}
    A.~J.~Bell and T.~J.~Sejnowski, ``An information-maximization approach to blind separation,''
    \textit{Neural Comput.}, vol.~7, no.~6, pp.~1129--1159, 1995.

    \bibitem{PascualMarqui1994}
    R.~D.~Pascual-Marqui, C.~M.~Michel, and D.~Lehmann,
    ``Low resolution electromagnetic tomography,''
    \textit{Int. J. Psychophysiol.}, vol.~18, no.~1, pp.~49--65, 1994.

    \bibitem{Nuwer1999}
    M.~R.~Nuwer \textit{et al.}, ``IFCN standards for digital recording of clinical EEG,''
    \textit{Electroencephalogr. Clin. Neurophysiol.}, vol.~106, pp.~259--261, 1998.

    \bibitem{Makeig2004}
    S.~Makeig \textit{et al.}, ``Mining event-related brain dynamics,''
    \textit{Trends Cogn. Sci.}, vol.~8, no.~5, pp.~204--210, 2004.

    \bibitem{Yao2001}
    D.~Yao, ``A method to standardize a reference of scalp EEG recordings to a point at infinity,''
    \textit{Physiol. Meas.}, vol.~22, no.~4, pp.~693--711, 2001.
    
    \bibitem{Fernandez-Ruiz2023}
    A.~Fernandez-Ruiz \textit{et al.} ``Over and above frequency: Gamma oscillations as units of neural circuit operations,'' \textit{Neuron}, vol.~111, no.~7, pp.~936--953, 2023.
    
    \bibitem{Pardo2025}
    M.~Pardo-Rodriguez \textit{et al.} ``Conscious breathing enhances bidirectional cortical-autonomic modulation: dynamics of EEG band power and heart rate variability,'' \textit{Front. Syst. Neurosci.,}, vol.~19, pp.~1--16, 2025.

    \bibitem{Thomson1982}
    D.~J.~Thomson, ``Spectrum estimation and harmonic analysis,''
    \textit{Proc. IEEE}, vol.~70, no.~9, pp.~1055--1096, 1982.

    \bibitem{HuangEtAl1998}
    N.~E.~Huang \textit{et al.}, ``The empirical mode decomposition and the Hilbert spectrum,''
    \textit{Proc. R. Soc. Lond. A}, vol.~454, pp.~903--995, 1998.

    \bibitem{Tallon-Baudry1997}
    C.~Tallon-Baudry \textit{et al.}, ``Oscillatory gamma-band (30--70 Hz) activity
    induced by a visual search task in humans,''
    \textit{J. Neurosci.}, vol.~17, no.~2, pp.~722--734, 1997.

    \bibitem{Moca2021}
    V.~V.~Moca \textit{et al.}, ``Time-frequency super-resolution with superlets,''
    \textit{Nat. Commun.}, vol.~12, p.~337, 2021.

    \bibitem{LeVanQuyen2001}
    M.~Le~Van~Quyen \textit{et al.}, ``Comparison of Hilbert transform and wavelet methods
    for the analysis of neuronal synchrony,''
    \textit{J. Neurosci. Methods}, vol.~111, no.~2, pp.~83--98, 2001.

    \bibitem{Vinck2011}
    M.~Vinck \textit{et al.}, ``An improved index of phase-synchronization for
    electrophysiological data,''
    \textit{NeuroImage}, vol.~55, no.~4, pp.~1548--1565, 2011.

    \bibitem{Granger1969}
    C.~W.~J.~Granger, ``Investigating causal relations by econometric models
    and cross-spectral methods,''
    \textit{Econometrica}, vol.~37, no.~3, pp.~424--438, 1969.

    \bibitem{Friston2003}
    K.~J.~Friston \textit{et al.}, ``Dynamic causal modelling,''
    \textit{NeuroImage}, vol.~19, no.~4, pp.~1273--1302, 2003.

    \bibitem{Canolty2006}
    R.~T.~Canolty \textit{et al.}, ``High gamma power is phase-locked
    to theta oscillations in human neocortex,''
    \textit{Science}, vol.~313, pp.~1626--1628, 2006.

    \bibitem{Gross2001}
    J.~Gross \textit{et al.}, ``Dynamic imaging of coherent sources,''
    \textit{Proc. Natl. Acad. Sci.}, vol.~98, no.~2, pp.~694--699, 2001.

    \bibitem{Mullen2015}
    T.~R.~Mullen \textit{et al.}, ``Real-time neuroimaging and cognitive monitoring
    using wearable dry EEG,''
    \textit{IEEE Trans. Neural Syst. Rehabil. Eng.}, vol.~23, no.~6, pp.~843--848, 2015.

    \bibitem{PionTonachini2019}
    L.~Pion-Tonachini \textit{et al.}, ``ICLabel: An automated electroencephalographic
    independent component classifier,''
    \textit{NeuroImage}, vol.~198, pp.~181--197, 2019.

    \bibitem{Ablin2018}
    P.~Ablin \textit{et al.}, ``Faster independent component analysis by preconditioning
    with Hessian approximations,''
    \textit{IEEE Trans. Signal Process.}, vol.~66, no.~15, pp.~4040--4049, 2018.

    \bibitem{Palmer2011}
    J.~A.~Palmer \textit{et al.}, ``Newton method for the ICA mixture model,''
    \textit{Proc. ICASSP}, 2008.

    \bibitem{Barachant2012}
    A.~Barachant \textit{et al.}, ``Multiclass brain--computer interface classification
    by Riemannian geometry,''
    \textit{IEEE Trans. Biomed. Eng.}, vol.~59, no.~4, pp.~920--928, 2012.

    \bibitem{Lawhern2018}
    V.~J.~Lawhern \textit{et al.}, ``EEGNet: a compact convolutional neural network
    for EEG-based brain--computer interfaces,''
    \textit{J. Neural Eng.}, vol.~15, no.~5, p.~056013, 2018.

    \bibitem{Schirrmeister2017}
    R.~T.~Schirrmeister \textit{et al.}, ``Deep learning with convolutional neural networks
    for EEG decoding and visualization,''
    \textit{Hum. Brain Mapp.}, vol.~38, no.~11, pp.~5391--5420, 2017.

    \bibitem{Song2022}
    Y.~Song \textit{et al.}, ``EEG conformer: Convolutional transformer for EEG
    signal decoding and visualization,''
    \textit{IEEE Trans. Neural Syst. Rehabil. Eng.}, vol.~31, pp.~710--719, 2022.

    \bibitem{Kostas2022}
    D.~Kostas \textit{et al.}, ``BENDR: using transformers and a contrastive
    self-supervised learning task to learn from massive amounts of EEG data,''
    \textit{Front. Hum. Neurosci.}, vol.~15, p.~653659, 2021.

    \bibitem{Jiang2024}
    W.~Jiang \textit{et al.}, ``Large brain model for learning generic representations
    with tremendous EEG data in BCI,''
    \textit{ICLR}, 2024.

    \bibitem{Michel2018}
    C.~M.~Michel and T.~Koenig, ``EEG microstates as a tool for studying the temporal
    dynamics of whole-brain neuronal networks,''
    \textit{NeuroImage}, vol.~180, pp.~577--593, 2018.

    \bibitem{Britz2010}
    J.~Britz \textit{et al.}, ``BOLD correlates of EEG topography reveal rapid
    resting-state network dynamics,''
    \textit{NeuroImage}, vol.~52, no.~4, pp.~1162--1170, 2010.

    \bibitem{Richman2000}
    J.~S.~Richman and J.~R.~Moorman, ``Physiological time-series analysis using
    approximate entropy and sample entropy,''
    \textit{Am. J. Physiol.}, vol.~278, no.~6, pp.~H2039--H2049, 2000.

    \bibitem{Tagliazucchi2012}
    E.~Tagliazucchi \textit{et al.}, ``Criticality in large-scale brain fMRI dynamics,''
    \textit{Front. Physiol.}, vol.~3, p.~15, 2012.

    \bibitem{Subasi2005}
    A.~Subasi, ``Automatic recognition of alertness level from EEG,''
    \textit{Expert Syst. Appl.}, vol.~28, no.~4, pp.~701--711, 2005.

    \bibitem{Perslev2021}
    M.~Perslev \textit{et al.}, ``U-Sleep: resilient high-frequency sleep staging,''
    \textit{npj Digit. Med.}, vol.~4, p.~72, 2021.

    \bibitem{Harmon-Jones2003}
    E.~Harmon-Jones and J.~J.~B.~Allen,
    ``Behavioral activation sensitivity and resting frontal EEG asymmetry,''
    \textit{J. Abnorm. Psychol.}, vol.~106, no.~1, pp.~159--163, 1997.

    \bibitem{Casali2013}
    A.~G.~Casali \textit{et al.}, ``A theoretically based index of consciousness
    independent of sensory processing and behavior,''
    \textit{Sci. Transl. Med.}, vol.~5, no.~198, p.~198ra105, 2013.

    \bibitem{Sitaram2017}
    R.~Sitaram \textit{et al.}, ``Closed-loop brain training: the science of neurofeedback,''
    \textit{Nat. Rev. Neurosci.}, vol.~18, no.~2, pp.~86--100, 2017.

  \end{thebibliography}
\end{frame}
